%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Club Member} % Role
    {BDAI (Be Data-literate, Advance with AI)} % Title
    {Seoul, S.Korea} % Location
    {Mar. 2026 - Feb. 2027 (Expected)} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Completed intensive curriculum on mathematical foundations for data science and data preprocessing techniques.}
        \item {Participated in end-to-end data modeling projects with a focus on model deployment and production-ready pipelines.}
        \item {Conducted comprehensive exploratory data analysis (EDA) and implemented machine learning models for various real-world datasets.}
      \end{cvitems}
    }

%---------------------------------------------------------

%---------------------------------------------------------
    \cventry
    {Mentor} % Role
    {University Innovation Program - Freshman Mentoring} % Title
    {Myongji University} % Location
    {Mar. 2025 - Dec. 2025} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Guided freshman students in the Convergence Software department to help them adapt to university life and academic requirements.}
        \item {Shared effective study strategies and foundational programming knowledge to support their early academic success.}
      \end{cvitems}
    }

%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
    {club member} % Role
    {COIN (Co-Insight Data Analysis Club)} % Title
    {Myongji University} % Location
    {Mar. 2024 - Dec. 2024} % Date(s) 
    {
      \begin{cvitems} % Description(s)
      \item {Engaged in weekly study sessions to deepen understanding of advanced machine learning algorithms and statistical methodologies.}
        \item {Collaborated on diverse data analysis projects covering the full pipeline from raw data EDA to machine learning modeling.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
