%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Project Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Primary Researcher} % Role
    {\href{https://github.com/lthofficial01/2025-olink-analyze-tool}{Client-Side Olink Proteomics Web Analyzer}} % Title
    {AIDALab, Myongji University} % Location 
    {Mar. 2025 - Dec. 2025} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Built a browser-local Olink NPX analysis workflow for sensitive biomedical data using React, TypeScript, Pyodide, Web Worker, and Plotly.}
        \item {Implemented file/schema handling, pivot, QC, PCA, DEP/volcano, missingness, ML baseline, and PPI network modules.}
        \item {Reduced evaluation leakage with train-only feature selection and improved browser stability through chunk loading and memory optimization.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Project Lead} % Role
    {\href{https://github.com/lthofficial01/2026-1-bigdata-sac-on-screen-recommendation}{SAC on Screen Regional Genre Recommendation Pipeline}} % Title
    {Big Data Project} % Location
    {2026} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Built a reproducible HDFS-to-Spark-to-Hive pipeline that combines performance reservation patterns with regional population data.}
        \item {Designed a region-level genre demand index and generated Top 3 content recommendations for each municipality.}
        \item {Implemented PySpark preprocessing, Hive external tables, HiveQL analysis, CSV export automation, and Matplotlib result visualization.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
